BurgerTown Presents: Open Adcess

### 2017-04-26 ideas.tex
updates?

>>>>

headoff guillotine. bullet: apply directly to the forehead. symbolic violence apply directly to the forehead ideology apply directly to the forehead ideology apply directly to the forehead ideology apply directly to the forehead ideology free market capitalism is the best path to prosperity apply directly to the forehead we have hired consultants to look at peer companies and establish a Market Wage. you are peing paid your market wage. it is a rational system. you would be happier if you only bought more consumer goods. but remember to pay sallie mae. then you need this job more. damn labor market is getting tight in this industry. if we don¿t strategically reduce aggregate demand we¿re going to have to start paying a market wage in this industry. tolerate concentrated private economic power. tolerate monopoly ownership of the businesses in your industry. tolerate monopsony. you¿re not going to change anything anyway. don¿t bother trying. be cynical. we have two interchangeable, equally neoliberal political parties. they¿re the same. don¿t vote. we¿re all working for the same capitalists anyway. industry ownership by single entities. phony competition. same fund controls all the companies in an industry, same company controls all the restaurants in a neighborhood. remember. we¿re all in this together. we all work for the man. fill in your linked in page. don¿t realize we¿re all working for different facets of the man. linked in pages would be boring if you just wrote ¿the man¿ so write these cute corporate names and remember their logos and visions. we¿re looking for a better cultural fit.
